%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%-------------------------------------------------------------------------------
  \cventry
    {Software Development Tech Lead} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Sep. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achievements:}
          \begin{itemize}
            \item {Cultivated and nurtured a meritocratic team culture.}
            \item {Created and maintained a psychologically safe space for team(Developers, Testers and BAs) to experiment and grow.}
            % Team 6 month Roadmap, clearly defined stories{objective, stakeholder, value proposition etc}, frequent(almost dil)
            \item {Implemented a streamlined SDLC process.}
          \end{itemize}
        \begin{itemize}
          \item {Designed and/or delivered various software systems to enable business needs:}
          \begin{itemize}
            \item {Ensure Life Investments subsidiary's overall compliance to SARB foreign investment exposure limit.}  
            \item {Enable management of model portfolios on investment platform.}
            \item {Distinguish Adults and Minor transaction minimums on investment platform.}
            \item {Support hedge funds in Regulation 28 validation.}
          \end{itemize}
        \end{itemize}
        \item {Key Responsibilities:}
        \begin{itemize}
          \item {Collaborate with the PO and BA to prioritise project requirements backlog.}
          \item {Collaborate with the team to decompose requirements into implementable software components.}
          \item {Mentor developers and testers.}
          \item {Manage team technical debt.}
          \item {Review software component designs and implementations.}
          \item {Design, Implement and Maintain software components.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Nov. 2018 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achievements:}
        \begin{itemize}
          \item {Defined and implemented a base framework to enable future implementations of Straight Through Online Transactions(STP) processing.}
          \item {Reduced manually processed additional contribution transactions by 50 to 60\% by automating it with the STP platform.}
        \end{itemize}
        \item {Key Responsibilities:}
        \begin{itemize}
          \item {Design and implement software systems to enable efficient and effective transactions processing.}
          \item {Code review software components implementations.}
          \item {Onboard other developers onto the team and the Transactions domain.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Jan. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Design and implement software systems to enable efficient and effective retirement transactions processing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
  {Systems Analyst} % Job title
  {Digiata} % Organization
  {Rosebank, South Africa} % Location
  {Dec. 2014 – Dec. 2015}% Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Contribute LINX, Stadium and Database solutions to a data migration platform.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
  {Information Technology Analyst} % Job title
  {KPMG} % Organization
  {Hatfield, South Africa} % Location
  {Jan. 2014 – Nov. 2014} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Assess the effectiveness of IT processes and risk management strategies against standards such as CMMI, King |||, COBIT and ITIL.}
    \end{cvitems}
  }

%---------------------------------------------------------

%  \cventry
%  {Systems Analyst} % Job title
%  {Digiata} % Organization
%  {Rosebank, South Africa} % Location
%  {Dec. 2014 – Dec. 2015}% Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%      \item {Products:}
%      \begin{itemize}
%        \item {Data Migration and Integration Pipeline}
%      \end{itemize}
%     \item {Key Responsibilities:}
%      \begin{itemize}
%        \item {Decompose technical requirements into solutions.}
%       \item {Design, implement and test LINX, Stadium and Database solutions for a data migration and integration platform.}
%      \end{itemize}
%    \end{cvitems}
%  }

  %---------------------------------------------------------
%  \cventry
%  {Information Technology Analyst} % Job title
%  {KPMG} % Organization
%  {Hatfield, South Africa} % Location
%  {Jan. 2014 – Nov. 2014} % Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%    \item {Key Responsibilities:}
%      \begin{itemize} 
%        \item {Assess the effectiveness of IT processes and risk management strategies against standards such as CMMI, King |||, COBIT and ITIL.}
%        \item {Develop key action plans for improvement of business and I.T environments, risk management frameworks and processes.}
%      \end{itemize}
%    \end{cvitems}
%  }

  %---------------------------------------------------------
\end{cventries}
