%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Development Tech Lead} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {March. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the delivery, design and/or implementation of various projects:}  
        \begin{itemize}
          \item {Enable operations and web teams to get automated and consistent transaction minimums validation for minors and adults.}
          \item {Enable operations and web teams to get automated and consistent Regulation 28 validation of transactions with hedge fund instruments.}
          \item {Enable organisation's Life Investments subsidiary to stay within the SARB foreign investment exposure limit.}
          \item {Enable operations team to manage model portfolios.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Nov. 2018 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the design and implementation of a base framework for Straight Through Online Transactions(STP) processing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Jan. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implement Scala RESTful APIs, relational database and Camunda workflows to automate retirement transactions.} 
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Systems Analyst} % Job title
  {Digiata} % Organization
  {Rosebank, South Africa} % Location
  {Dec. 2014 – Dec. 2015}% Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Contribute LINX, Stadium and Database solutions to a data migration platform.}
    \end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {Information Technology Analyst} % Job title
  {KPMG} % Organization
  {Hatfield, South Africa} % Location
  {Jan. 2014 – Nov. 2014} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Assess the effectiveness of IT processes and risk management strategies against standards such as CMMI, King |||, COBIT and ITIL.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
\headerquotestyle{Please visit my LinkedIn(Projects section) and Github profile linked above for project implementation details.} 


