%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%-------------------------------------------------------------------------------
  \cventry
    {Software Development Tech Lead} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Sep. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Products:}
        \begin{itemize}
          \item {Fund Administration System.}
          \item {Fund Pricing System.}
          \item {Instruction and Compliance Validation RESTful Microservices.}
          \item {Funds Platform Primitives RESTful Microservices.}
          \item {Residual Transactions Processor.}
          \item {Model Portfolio Management System.}
        \end{itemize}
        \item {Key Responsibilities:}
        \begin{itemize}
          \item {Create and maintain a psychologically safe space for developers and testers to experiment and grow.}
          \item {Collaborate with the PO and BA to prioritise project requirements backlog.}
          \item {Collaborate with the team to decompose requirements into implementable software components.}
          \item {Mentor developers and testers.}
          \item {Manage team technical debt.}
          \item {Review software component designs and implementations.}
          \item {Design, Implement and Maintain software components.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Nov. 2018 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Products:}
        \begin{itemize}
          \item {Straight Through Transactions Processing Platform.}
          \item {Additional Contribution Straight Through transaction.}
        \end{itemize}
        \item {Key Responsibilities:}
        \begin{itemize}
          \item {Design and Implement a base framework to enable the implementation of Straight Through Online Transactions processing.}
          \item {Onboard other developers onto the team and the Transactions domain.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Jan. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Products:}
        \begin{itemize}
          \item {Long running(2+ days) Transactions Processing Platform.}
          \item {Various Life products transaction automation.}
        \end{itemize}
        \item {Key Responsibilities:}
        \begin{itemize}
          \item {Design and implement Scala RESTful APIs, relational database and Camunda workflows to automate retirement transactions.}
          \item {Onboard other developers onto the team and the Transactions domain.}
        \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%  {Systems Analyst} % Job title
%  {Digiata} % Organization
%  {Rosebank, South Africa} % Location
%  {Dec. 2014 – Dec. 2015}% Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%      \item {Products:}
%      \begin{itemize}
%        \item {Data Migration and Integration Pipeline}
%      \end{itemize}
%     \item {Key Responsibilities:}
%      \begin{itemize}
%        \item {Decompose technical requirements into solutions.}
%       \item {Design, implement and test LINX, Stadium and Database solutions for a data migration and integration platform.}
%      \end{itemize}
%    \end{cvitems}
%  }

  %---------------------------------------------------------
%  \cventry
%  {Information Technology Analyst} % Job title
%  {KPMG} % Organization
%  {Hatfield, South Africa} % Location
%  {Jan. 2014 – Nov. 2014} % Date(s)
%  {
%    \begin{cvitems} % Description(s) of tasks/responsibilities
%    \item {Key Responsibilities:}
%      \begin{itemize} 
%        \item {Assess the effectiveness of IT processes and risk management strategies against standards such as CMMI, King |||, COBIT and ITIL.}
%        \item {Develop key action plans for improvement of business and I.T environments, risk management frameworks and processes.}
%      \end{itemize}
%    \end{cvitems}
%  }

  %---------------------------------------------------------
\end{cventries}
