%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%-------------------------------------------------------------------------------
  \cventry
    {Software Development Tech Lead} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Sep. 2019 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \begin{itemize}
          \item {Cultivated and nurtured a meritocratic team culture.}
          \item {Created and maintained a psychologically safe space for team(Developers, Testers and Business Analysts) to experiment and grow.}
          \item {Implemented a streamlined SDLC process.}
          \item {Mentored developers and testers.}
          \item {Managed team technical debt.}
          \item {Reviewed software component designs and implementations.}
          \item {Designed and delivered various software systems to enable business needs.}
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Nov. 2018 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \begin{itemize}
          \item {Defined and implemented a base framework to enable future implementations of Straight Through Online Transactions(STP) processing.}
          \item {Reduced manually processed additional contribution transactions by 50 to 60\% by automating it with the STP platform.}
          \item {Designed and implement software systems to enable efficient and effective transactions processing.}
          \item {Reviewed software component designs and implementations.}
          \item {Onboard other developers onto the team and the Transactions domain.}
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Allan Gray Proprietary Limited} % Organization
    {Cape Town, South Africa} % Location
    {Jan. 2016 - Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \begin{itemize}  
          \item {Designed and implemented software systems to enable efficient and effective retirement transactions processing.}
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Systems Analyst} % Job title
    {Digiata} % Organization
    {Rosebank, South Africa} % Location
    {Dec. 2014 – Dec. 2015}% Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \begin{itemize}  
          \item {Contributed LINX, Stadium and Database solutions to a data migration platform.}
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Information Technology Analyst} % Job title
    {KPMG} % Organization
    {Hatfield, South Africa} % Location
    {Jan. 2014 – Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \begin{itemize}  
          \item{Assessed the effectiveness of IT processes and risk management strategies against standards such as CMMI, King III, COBIT and ITIL.}
        \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
\headerquotestyle{Please visit my LinkedIn(Projects section) and GitHub profile linked above for project implementation details.}

