%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}
%---------------------------------------------------------
  \cvskill
    {Computation Models} % Category
    % Skills
    {\skilltypestyle{Medium proficiency:} Declarative(Functional), Stateful(Imperative), Stateful(Object Orientated).} 
  \cvskill
    {Programming Languages} % Category
    % Skills
    { \skilltypestyle{Medium proficiency:} Python, Scala. } 
  \cvskill
    {} % Category
    % Skills
    { \skilltypestyle{Low proficiency:} Bash, C, Java, JavaScript, HTML.} 
  \cvskill
    {Architectural Patterns} % Category
    % Skills
    { \skilltypestyle{High proficiency:} Domain Driven Design(DDD), Event Driven Design, Test-Driven Development.}
  \cvskill
    {} % Category
    % Skills
    { \skilltypestyle{High proficiency:} Microservices, REST.}
  \cvskill
    {} % Category
    { \skilltypestyle{Medium proficiency:} Model View Controller.} 
  \cvskill
    {} % Category
    { \skilltypestyle{Low proficiency:} Command Query Responsibility Segregation.} 
%---------------------------------------------------------
  \cvskill
    {Frameworks and Libraries} % Category
    % Skills
    { \skilltypestyle{Medium proficiency:} Dropwizard, RabbitMQ.} 
  \cvskill
    {} % Category
    % Skills
    { \skilltypestyle{Low proficiency:} Django, Flask, RabbitMQ, React.} 
  
%---------------------------------------------------------
  \cvskill
  {Databases} % Category
  % Skills
  { \skilltypestyle{Medium proficiency:} Flyway, Microsoft SQL Server, SQL, TSQL.} 
  \cvskill
  {} % Category
  % Skills
  { \skilltypestyle{Low proficiency:} PostgresSQL, PL/SQL, SQLAlchemy.} 
%---------------------------------------------------------
  \cvskill
    {Process Automation}
    {\skilltypestyle{Medium proficiency:} Business Process Model and Notation(BPMN), Camunda.}
%---------------------------------------------------------
  \cvskill
    {DevOps} % Category
    {\skilltypestyle{Medium proficiency:} Docker, GitLab CI/CD, Kubernetes.} % Skills
  \cvskill
    {} % Category
    { \skilltypestyle{Low proficiency:} GitHub Actions, Make.} 
%---------------------------------------------------------
  \cvskill
  {Version Control} % Category
  {\skilltypestyle{High proficiency:} Git, Git flow.} % Skills
%---------------------------------------------------------
  \cvskill
  {Project Management} % Category
  {\skilltypestyle{Medium proficiency:} Jira.} % Skills
\end{cvskills}